---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    fig.width: 15
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `brfss2013`. Delete this note when before you submit 
your work. 

```{r load-data}
load("brfss2013.RData")
# load("~/workspace/selfStudy/online_courses/coursera/intro_probability_duke/week5_project/brfss2013.RData")
```



* * *

## Part 1: Data
The data file has 491775 observations of 330 variables. There is a lot of information can be mining from the data. However, we will focus mainly at Income Level, Physical Activity, Health Care Access, and Inadequate Sleep.

* * *

## Part 2: Research questions

**Research quesion 1:**
Does the Income Level has connection with Physical Activity.

**Research quesion 2:**
Does the Income Level has connection with Healhcare Access.

**Research quesion 3:**
Does the Income Level has connection with High Blood Pressure.

* * *

## Part 3: Exploratory data analysis

**Research quesion 1:**
Does the Income Level has connection with Physical Activity.

Now plot the bar char of how many people do exercies in each income level.
```{r plot-bar-income-exercises}
brfss2013 %>% select(income2, exerany2) %>% filter(!is.na(income2), !is.na(exerany2)) -> income_exercises
ggplot(data = income_exercises, aes(x = income2, fill = exerany2)) + geom_bar() + scale_x_discrete(labels = c(" < 10k$", " < 15k$", " < 20k$", " < 25k$", " < 35k$", " < 50k$", " < 75k$", " >= 75k$"))
```

We can see that the higher they earn, the more they do exercises. 


**Research quesion 2:**
Does the Income Level has connection with Health Care Access.
```{r}
brfss2013 %>% select(income2, hlthpln1) %>% filter(!is.na(income2), !is.na(hlthpln1)) -> income_healthcare
ggplot(data = income_healthcare, aes(x = income2, fill = hlthpln1)) + geom_bar() + scale_x_discrete(labels = c(" < 10k$", " < 15k$", " < 20k$", " < 25k$", " < 35k$", " < 50k$", " < 75k$", " >= 75k$"))
```

The more they earn, the more they have access to health care system.


**Research quesion 3:**
Does the Income Level has connection with High Blood Pressure.
```{r}
brfss2013 %>% select(income2, bphigh4) %>% filter(!is.na(income2), !is.na(bphigh4)) -> income_pbhigh
ggplot(data = income_pbhigh, aes(x = income2, fill = bphigh4)) + geom_bar() + scale_x_discrete(labels = c(" < 10k$", " < 15k$", " < 20k$", " < 25k$", " < 35k$", " < 50k$", " < 75k$", " >= 75k$"))
```

The upper middle class and the richest has less cardiovascular diseases.
